Model- polygenic version

### 2020-03-31 analysis/index.Rmd
sparse model description

# Model
  [polygenic model](polygenic_model.html)

@@

>>>>

# Model
  * [Polygenic model](polygenic_model.html)
  * [Sparse model](sparse_model.html)

@@

# References
  * VEB-boost
    * [Problem description](VEB-boost-fitting.html)
    * Andrew's [software](https://github.com/andrewg3311/VEB.Boost) and [workflowr website](https://andrewg3311.github.io/VEB-Boost-workflowR/VEB_Boost_Derivation.html)

### 2020-03-31 analysis/polygenic_model.Rmd
fix results display bug
sparse model description

---
title: "Model"
author: "Siming Zhao"
date: "10/29/2019"
output: html_document
---

@@

## Polygenic Model
 $$Y = \tilde{X}\gamma + G\theta + \epsilon$$
$Y$: quantitative traits, $N$ x 1 vector, $N$ is number of individuals  
$\tilde{X}$: imputed gene expression (standardized). $N$ x $J$ matrix, $J$ is number of genes.  
$G$: genotype (standardized). $N$ x $M$ matrix, $M$ is number of SNPs.  
$\gamma$: effect sizes for $\tilde{X}$,  $\gamma_j$, effect size for gene $j$.

>>>>

---
title: "Model- polygenic version"
author: "Siming Zhao"
date: "10/29/2019"
output: html_document
---

@@

## Polygenic Model
 $$Y = \tilde{X}\gamma + G\theta + \epsilon$$
$Y$: quantitative traits, $N$ x 1 vector, $N$ is number of individuals  
$\tilde{X}$: cis-gene expression (the genetic component of expression). $N$ x $J$ matrix, $J$ is number of genes.  
$G$: genotype (standardized). $N$ x $M$ matrix, $M$ is number of SNPs.  
$\gamma$: effect sizes for $\tilde{X}$,  $\gamma_j$, effect size for gene $j$.
